### 2016-08-31 notions.tex
no message

\subsection{Notions of Privacy}
One can also consider the orthogonal notion of privacy for a
data structure. \jnote{I am still hoping that we can treat data structures
at an even more general level than set-representation data structures.}
We formalize two types of privacy notions. The first captures
a ``one-wayness'' property that (informally) requires that
the representation of some set~$S$ does not make it any easier for an attacker
to learn an element of~$S$.
The second definition
captures a flavor of semantic security, essentially requiring that $M$ and $\pub$ do
not leak any information about the set~$S$ they represent beyond
what is captured in some explicit leakage function.

@@

\jnote{I don't know if I like the one-wayness definition any more; it seems a bit
ad hoc. And why do we care about one-wayness, anyway? Instead, I give
two versions of semantic security.}

>>>>

\subsection{Privacy}
\jnote{Define appropriate notion of min-entropy for our setting.
Define one-wayness.}

One can also consider the orthogonal notion of \emph{privacy} for a
data structure. \jnote{I am still hoping that we can treat data structures
at an even more general level than set-representation data structures.}
We formalize two types of privacy notions. The first captures
a ``one-wayness'' property that (informally) requires that
the representation of some set~$S$ does not make it any easier for an attacker
to learn an element of~$S$.
The second definition
captures a flavor of semantic security, essentially requiring that $M$ and $\pub$ do
not leak any information about the set~$S$ they represent beyond
what is captured in some explicit leakage function.

@@

%\jnote{I don't know if I like the one-wayness definition any more; it seems a bit
%ad hoc. And why do we care about one-wayness, anyway? Instead, I give
%two versions of semantic security.}
